Statistical Grand Slams

### 2023-12-15 Lahman Analysis/Formal Analysis/Draft1.qmd
Edited through data

The next parameter we considered which affects $\pi_{nip}$ was $\beta_n$ which represents the effect centered age (the player's age minus 30) had on player $n$'s ability to hit HR's. This topic was briefly touched upon in @sec-BaseBack, where we discussed how a player's age can impact their their strategy and physical prowess. These ideas are well demonstrated in @fig-HR.By.Age.20to40. In @fig-HR.By.Age.20to40, one can easily see that, in general, players' ability to hit HR's improves over the course of their career and peaks when players reach about 30 years old. After this peak, a player's ability starts to decline for the rest of their career. We chose to center the the age of the all players at 30 for several reasons. The first was that roughly the mean and the median ages in the data was 30. Second, having a centered age makes interpreting $\beta_n$ easier. The value of $\beta_n$ represents how changes away from the centered age affects player $n$'s probability of hitting a HR, $\pi_{nip}$. In a normal GLM's, $\beta_n$ would not be able to adapt to each player, $n$, as it does in our model. It would only be able to consider how aging affects the average player's HR probability and then apply that effect to all players. This implicitly assumes that each player is affected identically by changes in age. In contrast, we employ multilevel modeling techniques to our model where $\beta_n\sim Normal(\mu_1,\sigma_1)$, $\mu_1\sim Normal(0,0.1)$, and $\sigma_1\sim Exponential(10)$. Similar to understanding $\alpha_n$, we can interpret $\beta_n$ as a collection of distributions corresponding to the different values of its hyper-priors $\mu_1$ and $\sigma_1$ and their corresponding likelihoods. We chose a normal distribution for $\mu_1$ for reasons similar to $\mu_0$. It makes interpretation easier and there is precedent in the literature. Again, for similar reasons to $\sigma_0$ we chose $\sigma_1$ to be exponentially distriubted. This ensured that $\sigma_1$ would not be negative and that the bulk of the possible values of $\sigma_1$ would be clustered near 0. With the distributions calculated for $\beta_n$ we can now use $\beta_n$ as the prior and combine it with the player data to generate the posterior using Bayes theorem. We repeat this process for all 657 players considered to get a unique distribution for each player $\beta_n$. This means that each player, $n$ has a unique aging coefficient which represents how aging effects them. Whatever value in $\beta_n$ has the maximum likelihood, that's what we used to generate our predictions for inference in @sec-Results.

Similarly $\eta_n$ is the effect that player $n$'s squared age has on his probability of hitting a HR in an AB. The purpose of this squared term is to capture the non-linear relationship between hitting a HR and player $n$'s age. It is apparent in both @fig-HR.By.Age.20to40 and @fig-HR.By.Age.All that there is a parabolic relationship between age and player $n$'s ability to hit HR's. This ability appears to rise steadily for the average player until it reaches its apex when the player is roughly 30 years old. Then, in the seasons where the player is more than 30-years-old we see a decline in HR probabilities. The shape we are left with, as can be seen in @fig-HR.By.Age.20to40, is one of an upside-down parabola. Thus, by including this squared age effect, we are able to capture that unique relationship. However, as one can easily notice in @fig-HR.By.Age.20to40, the overall shape is parabolic but for ages past 37 the data begins to trend upwards. Likely, this trend upwards is due to players who have above average skill. That is, players who have earned massive contracts because they were so much better than the average player in their prime earned large multi-million dollar contracts and teams do not want to waste the this money so they play these players. So, we are then left with this group of outlying players who do not follow the trend of data at any point over their career, but it only became noticeable after the other, more normal, players disappeared from the considered sample. Returning to the parameter $\eta_n$, it is nearly impossible to interpret what it is doing because it describes the effect of centered age squared on HR probability $\pi$, and centered age squared on its own is already almost a meaningless concept. Therefore, it is best understood that this term simply accounts for the non-linearity we see in the data and not become too concerned with understanding its estimates. However, it is easy to justify our choice for the priors and hyper-priors of $\eta_n$, $\mu_2$, and $\sigma_2$, respectively. We chose $\eta_n\sim Normal(\mu_2,\sigma_2)$ for the same reasons discussed for both $\alpha_n$ and $\beta_n$: we wanted a multilevel model which described how individual players were impacted by the parameters. We chose $\mu_2\sim Normal(0,0.01)$ because we assumed that there would be a negative effect so small that it would be very close to zero. Further, any distinction to the slightly negative of zero would be hard to justify and, in essence, arbitrary. Therefore, we went with the mean of 0 and the standard deviation of 0.01 to account for any players who have a more or less extreme non-linearity to their trajectories. That is, higher or lower peaks and troughs throughout their career for their probability $\pi$. We chose $\sigma_2\sim Exponential(100)$ because standard deviations cannot be negative, which the exponential distribution lends itself nicely to. Furthermore, the exponential distribution with a parameter of 100 is very concentrated near 0. Since we know that the coefficient of $\eta_n$ is likely to be very small since it is being multiplied by the age squared (which can be up over 100). Thus, we can be confident that our standard deviation will end up being small for our estimate. This means that the estimates our model generates will be close to 0.

Another parameter of our model is $\delta_p$, which describes the effect playing in ballpark $p$ in year $i$ has player $n$'s HR probability, $\pi_{nip}$. There are 88 different ballparks we considered, and we generated an estimate for each of them. This was discussed in @sec-BaseBack, where we highlighted that players in certain ballparks are more likely to hit HR's than in others because of the different dimensions of the outfield fences. Furthermore, we know that these parks will effect players differently because teams play at different ballparks with varying frequency. For example, players will play 81 of their games at their home-stadium and 81 at various other ballparks known as "on the road." Thus, the home-stadium that player $n$ plays at is an important factor for their HR probability, $\pi$, because player $n$ plays many more games at his home-stadium compared to any other ballpark. In our model, we have estimated $\delta_p$ as an intercept term which captures the effect that playing at stadium $p$ has on HR probability, $\pi$. Stadiums like Great American Ballpark (index=33) tend to have a better HR effect than stadiums such as Cleveland Stadium (index=19). By better, we mean that it the probability of hitting a HR is higher at Great American Ballpark compared to Cleveland Stadium because our model interprets hitting a HR as a success. Interpreting $\delta_p$ is much easier than the previous two parameters. It simply states, on the logit scale, how the park effects the underlying probability of hitting a HR, $\pi$. In addition, $\delta_p$ takes advantage of multilevel modeling since we have hyper-priors, $\mu_5$ and $\sigma_5$. We have purposely set the hyper-prior of $\mu_5\sim Normal(0,0.01)$ with mean 0 because we assume that parks in the aggregate will not have an effect on a player's ability to hit HR's. That is, on average, for every Cleveland Stadium there exists a Great American Ballpark which acts as a counterweight and makes the aggregate effect 0. There is no formal justification for this, it is just an assumption that we make based on our preliminary exploration and our understanding that ownership (who controls the dimensions of the stadium) are not particularly biased to any ballpark size which means that we should see good variation between parks. Further, we assume that a fair standard deviation for $\mu_5$ is 0.01 because on the logistic scale, this means that we could see about a two percent change in the probabilities between any given stadiums. At most we would see a 4% difference. We chose a standard deviation for $\delta_p$ to be $\sigma_5\sim Exponential(10)$ for similar reasons to all of the other $\sigma_i$'s. The exponential distribution cannot be negative, which we need for standard deviations. Further, we know that the effect of each park will probably not be huge because, although there is deviation, there is not extreme deviation between parks that makes some "unfair." Thus, with our parameter of 10 for the exponential distribution we are being fairly confident with our model about our estimates of the priors, in that we do not allow much deviation from our mean of 0 unless the data strongly suggests otherwise.

Our final parameter, $\xi_i$ represents the change in the underlying probability of player hitting a HR in the year $i$. This stems mostly from the observation in @fig-HRByYear which shows a steep increase in the amount of HR's hit per year across any subset of years considered. Further, we can tell from @fig-pByYear that these additional HR's are not just the product of expansion teams creating more opportunities for players to hit more HR's. @fig-pByYear shows that the proportion of AB's which are HR's have risen steadily over the period considered which suggests that players' probabilities have been changing. This means that there is an underlying change in the $\pi$ depending on the year considered. The reason for this change is irrelevant. It could be because batters are becoming better or pitchers are getting worse, or it could be some other unrelated reason. Regardless, we can see that there is an increase and we need to account for this in our estimates for $\pi$ of player $n$. Thus, we include $\xi_i$ to represent the effect that playing in a certain year will have on the player's ability to hit a HR. We set the hyper-prior of $\xi_i$ as $\mu_6\sim Normal(0, 0.25)$ because we can see that the HR proportion change year over year in @fig-pByYear by only fractions of a percent. Thus, when we set our prior with mean 0 and standard deviation of 0.25, we are saying that we expect most year of year variation to be from \[-4, -3\] on the logit scale. On the normal this is \[0.018, 0.047\] which means that we would expect at most a change of 3% year over year. This is much larger than we would actually anticipate in a change but it allows the model to learn from the data to learn from the data more since we are unsure of exactly what the change beyond knowing that there is a change year over year. Furthermore, we set the hyper-prior $\sigma_6\sim Exponential(10)$ for the same reasons mentioned during the other $\sigma_i$'s. The exponential distribution ensures that we never have a negative estimate for our standard deviation of $\xi_i$ and having a parameter value of 10 for $\sigma_6$ allows the data to be fairly concentrated near 0 which is what we would expect for a year over year effect.

Compared to most GLM's, this model ([@eq-model]) we have created is massive. It has 2,116 parameters. It has 657 different $\alpha, \beta,$ and $\eta$'s estimated for each player. It has 88 $\delta$'s for each park and 47 $\xi$'s for each year. Finally, it has 10 different $\mu$'s and $\sigma$'s for the different hyper-priors. All together, totaling 2,116 parameters. This gargantuan size is what allows such powerful inference for our model. Even though the data on each player individually is sparse, since there is so much data available for the model to take in beyond that player and the model uses many simulations to create estimates, this allows our model to make strong inferences to be made concerning future performance.

@@

The goal of our model, as described in @eq-model, @eq-priors, and @eq-hyperpriors, was to be able to adaptively predict player $n$'s HR's. That is, we wished to create a model that would predict player $n$'s HR's and would adapt these predictions to be unique to player, $n$, the park played at, $p$, and the year played, $i$. To check the fit of their model, Fellingham and Fisher (2017) selected popular players (such as Hank Aaron and Barry Bonds) as a representative sample of the player population. However, the problem with this approach is that Fellingham and Fisher (2017) have selected players who are phenomenal hitters and generally outliers in the data. For example, Barry Bonds currently holds the single season and career HR records. Which means that he has the most HR's hit in one season and the most hit over the course of a career compared to all people who have every played in MLB. The career HR record he holds was previously held by Hank Aaron. Obviously, this sample of players is not representative of the population of players considered by Fellingham and Fisher (2017). So, while it may make the paper more enjoyable to read, it does not provide use with a rigorous understanding of the general fit of this model. We believe that a random sample should have been used to examine the fit of their model since it would give a better sense of overall model fit. Which, is exactly what we did in this paper. From the 657 players considered, we used R to select four random players to see how our model both fits and adapts to the different careers of players. These players are: Robin Yount ([@sec-yount]), Pat Tabler ([@sec-tabler]), and Kendrys Morales([@sec-morales]).

@@

Furthermore, we chose to examine $\pi_{nip}$ relative to centered age for all figures. This is because centered age corresponds directly to the parameters $\beta, \eta,$ and $\xi$ in our model ([@eq-model]). It should be obvious why centered age corresponds to $\beta$ and $\eta$. However, the reason we know that centered age corresponds to $\xi$ directly is because players are only an age for one season. Thus, if we are given a year and player $n$'s corresponding age we can deduce the year for all ages of the player. This means that the year-over-year effect, which $\xi$ captures, is directly present in the figures. The parameters $\alpha$ and $\delta$ work more in the background of the predictions presented in the figures. We leave the discussion of each to when they appear in the figures of certain players.

@@

>>>>

The next parameter we considered which affects $\pi_{nip}$ was $\beta_n$ which represents the effect centered age (the player's age minus 30) had on player $n$'s ability to hit HR's. This topic was briefly touched upon in @sec-BaseBack, where we discussed how a player's age can impact their their strategy and physical prowess. These ideas are well demonstrated in @fig-HR.By.Age.20to40. In @fig-HR.By.Age.20to40, one can easily see that, in general, players' ability to hit HR's improves over the course of their career and peaks when players reach about 30 years old. After this peak, a player's ability starts to decline for the rest of their career. We chose to center the the age of the all players at 30 for several reasons. The first was that roughly the mean and the median ages in the data was 30. Second, having a centered age makes interpreting $\beta_n$ easier. The value of $\beta_n$ represents how changes away from the centered age affects player $n$'s probability of hitting a HR, $\pi_{nip}$. In a normal GLM's, $\beta_n$ would not be able to adapt to each player, $n$, as it does in our model. It would only be able to consider how aging affects the average player's HR probability and then apply that effect to all players. This implicitly assumes that each player is affected identically by changes in age. In contrast, we employ multilevel modeling techniques to our model where $\beta_n\sim Normal(\mu_1,\sigma_1)$, $\mu_1\sim Normal(0,0.1)$, and $\sigma_1\sim Exponential(10)$. Similar to understanding $\alpha_n$, we can interpret $\beta_n$ as a collection of distributions corresponding to the different values of its hyper-priors $\mu_1$ and $\sigma_1$ and their corresponding likelihoods. We chose a normal distribution for $\mu_1$ for reasons similar to $\mu_0$. It makes interpretation easier and there is precedent in the literature. Furthermore, we chose it to have a mean of 0 because we assume that there is only a slighly poitive increase in HR probability year over year, which is close enough to zero that we let the data speak for itself. Again, for similar reasons to $\sigma_0$ we chose $\sigma_1$ to be exponentially distriubted. This ensured that $\sigma_1$ would not be negative and that the bulk of the possible values of $\sigma_1$ would be clustered near 0. With the distributions calculated for $\beta_n$ we can now use $\beta_n$ as the prior and combine it with the player data to generate the posterior using Bayes theorem. We repeat this process for all 657 players considered to get a unique distribution for each player $\beta_n$. This means that each player, $n$ has a unique aging coefficient which represents how aging effects their HR probability. Whatever value in $\beta_n$ has the maximum likelihood, that's what we used to generate our predictions for inference in @sec-Results.

Similarly $\eta_n$ is the effect that player $n$'s squared age has on his probability of hitting a HR in an AB. The purpose of this squared term is to capture the non-linear relationship between hitting a HR and player $n$'s age. It is apparent in both @fig-HR.By.Age.20to40 and @fig-HR.By.Age.All that there is a parabolic relationship between age and player $n$'s ability to hit HR's. This ability appears to rise steadily for the average player until it reaches its apex when the player is roughly 30 years old. Then, in the seasons where the player is more than 30 years old we see a decline in HR probabilities. The shape we are left with, as can be seen in @fig-HR.By.Age.20to40, is one of an upside-down parabola. Thus, by including this squared age effect, we are able to capture that unique relationship. However, as one can easily notice in @fig-HR.By.Age.20to40, the overall shape is parabolic but for ages past 37 the data begins to trend upwards. Likely, this trend upwards is due to players who have above average skill remaining in MLB beyond their average counterparts. That is, players who have earned massive contracts because they were so much better than the average player in their prime earned large, multimillion dollar, contracts and teams do not want to waste the this money so they play these players. So, we are then left with this group of outlying players who do not follow the trend of data at any point over their career, but it only became noticeable after the other, more normal, players disappeared from the considered sample.

Returning to the parameter $\eta_n$, it is nearly impossible to interpret what its meaning because it describes the relationship between centered age squared and HR probability. Centered age squared on its own is already almost a meaningless concept. Therefore, it is best understood that this term simply accounts for the non-linearity we see in the data and not become too concerned with interpreting its estimates. However, it is easy to justify our choice for the priors and hyper-priors of $\eta_n$, $\mu_2$, and $\sigma_2$, respectively. We chose $\eta_n\sim Normal(\mu_2,\sigma_2)$ for the same reasons discussed for both $\alpha_n$ and $\beta_n$: we wanted a multilevel model which described how individual players were impacted by the parameters. We chose $\mu_2\sim Normal(0,0.01)$ because we assumed that there would be a negative effect so small that it would be very close to zero. Further, any distinction to the slightly negative of zero would be hard to justify and, in essence, arbitrary. Therefore, we went with the mean of 0 and the standard deviation of 0.01 to account for any players who have a more or less extreme non-linearity to their trajectories. That is, higher or lower peaks and troughs throughout their career for their probability $\pi$. We chose $\sigma_2\sim Exponential(100)$ because standard deviations cannot be negative, which the exponential distribution lends itself nicely to. Furthermore, the exponential distribution with a parameter of 100 is very concentrated near 0. Since we know that the coefficient of $\eta_n$ is likely to be very small since it is being multiplied by the age squared (which can be over 100). Thus, we can be confident that our standard deviation will end up being small for our estimate. This means that the estimates our model generates for $\eta_n$ will be distributions highly concentrated near 0 until the data for player $n$ informs otherwise through Bayes theorem. This leaves that each player, $n$ with another unique aging coefficient which represents how non-linear aging effects their HR probability. Whatever value in $\eta_n$ has the maximum likelihood, that's what we used to generate our predictions for inference in @sec-Results.

Another parameter of our model is $\delta_p$, which describes the effect playing in ballpark $p$ has a player's HR probability. There are 88 different ballparks we considered, and we generated an estimate for each of them. This was discussed in @sec-BaseBack, where we highlighted that players in certain ballparks are more likely to hit HR's than in others because of the different dimensions of the outfield fences and the different altitude of the parks. Furthermore, we know that these parks will effect players differently because teams play at different ballparks with varying frequency. For example, players will play 81 of their games at their home-stadium and 81 at various other ballparks known as "on the road." Thus, the home-stadium that player $n$ plays at is an important factor for their HR probability, $\pi$, because player $n$ plays many more games at his home-stadium compared to any other ballpark. In our model, we have estimated $\delta_p$ as an intercept term and it takes advantage of multilevel modeling since we have hyper-priors, $\mu_5$ and $\sigma_5$. We have purposely set the hyper-prior of $\mu_5\sim Normal(0,0.01)$ with mean 0 because we assume that parks in the aggregate will not have an effect on a player's ability to hit HR's. There is no formal justification for this, it is just an assumption that we make based on our preliminary exploration and our understanding that ownership (who controls the dimensions of the stadium) are not particularly biased to any ballpark size or location which means that we should see good variation between parks. We chose a standard deviation for $\delta_p$ to be $\sigma_5\sim Exponential(10)$ for similar reasons to all of the other $\sigma_i$'s. The exponential distribution cannot be negative, which we need for standard deviations. Further, we know that the effect of each park will probably not be huge because, although there is deviation, there is not extreme deviation between parks that makes some "unfair" to play at. With the distributions calculated for $\delta_p$ (similar to every other multilevel parameter) we can now use $\delta_p$ as the prior and combine it with the player data to generate the posterior using Bayes theorem. We repeat this process for every park $p$ to generate the posterior distribution of possible effects that playing at park $p$ has on a player's HR probability. Whichever value in $\delta_p$ has the maximum likelihood, that is what we use to generate our predictions for inference in @sec-Results.

Our final parameter, $\xi_i$ represents the change in the underlying probability of hitting a HR in the year $i$. This stems mostly from the observation in @fig-HRByYear which shows a steep increase in the amount of HR's hit per year across any subset of years considered. Further, we can tell from @fig-pByYear that these additional HR's are not just the product of expansion teams creating more opportunities for players to hit more HR's. @fig-pByYear shows that the proportion of AB's which are HR's have risen steadily over the period considered which suggests that players' probabilities have been changing. This means that there is an underlying change in the $\pi$ depending on the year considered. Regardless of the reason for this change, we can see that there is an increase and we need to account for this in our estimates for $\pi$ for player $n$. Thus, we include $\xi_i$ to represent the effect that playing in year $i$ will have on a player's ability to hit a HR. We set the hyper-prior of $\xi_i$ as $\mu_6\sim Normal(0, 0.25)$ because we can see that the HR proportion change year over year in @fig-pByYear by only fractions of a percent. Thus, when we set our prior with mean 0, we are saying that we expect most year over year variation to be low and we would rather have the data speak through in the posterior compared to use setting a negligibly small prior. Furthermore, we set the hyper-prior $\sigma_6\sim Exponential(10)$ for the same reasons mentioned during the other $\sigma_i$'s. The exponential distribution ensures that we never have a negative estimate for our standard deviation of $\xi_i$, and having a parameter value of 10 for $\sigma_6$ allows the data to be fairly concentrated near 0 which is what we would expect for a year over year effect. With the distributions calculated for $\xi_i$ (similar to every other multilevel parameter) we can now use $\xi_i$ as the prior and combine it with the player data to generate the posterior using Bayes theorem. We repeat this process for every year $i$ to generate the posterior distribution of possible effects that playing in year $i$ has on a player's HR probability. Whichever value in $\xi_i$ has the maximum likelihood, that is what we use to generate our predictions for inference in @sec-Results.

Compared to most GLM's, this model ([@eq-model]) we have created is massive. It has 2,116 parameters. It has 657 different $\alpha, \beta,$ and $\eta$'s estimated for each player. It has 88 $\delta$'s for each park and 47 $\xi$'s for each year. Finally, it has 10 different $\mu$'s and $\sigma$'s for the different hyper-priors. All together, totaling 2,116 parameters. This gargantuan size is what allows such powerful inference for our model. Even though the data on each player individually is sparse, since there is so much data available for the model to take in beyond that player and the model uses many simulations to create estimates, this allows our model to make strong inferences concerning future performance.

@@

The goal of our model, as described in @eq-model, @eq-priors, and @eq-hyperpriors, was to be able to adaptively predict player $n$'s HR's. That is, we wished to create a model that would predict player $n$'s HR's and would adapt these predictions to be unique to player, $n$, the park played at, $p$, and the year played, $i$. To check the fit of their model, Fellingham and Fisher (2017) selected popular players (such as Hank Aaron and Barry Bonds) as a representative sample of the player population. However, the problem with this approach is that Fellingham and Fisher (2017) have selected players who are phenomenal hitters and generally outliers in the data. For example, Barry Bonds currently holds the single season and career HR records. Which means that he has the most HR's hit in one season and the most hit over the course of a career compared to all people who have ever played in MLB. The career HR record he holds was previously held by Hank Aaron, who now sits second on the list. Obviously, this sample of players is not representative of the population of players considered by Fellingham and Fisher (2017). So, while it may make the paper more enjoyable to read, it does not provide use with a rigorous understanding of the general fit of this model. We believe that a random sample should have been used to examine the fit of their model since it would give a better sense of overall model fit. Which, is exactly what we did in this paper. From the 657 players considered, we used R to select four random players to see how our model both fits and adapts to the different careers of players. These players are: Robin Yount ([@sec-yount]), Pat Tabler ([@sec-tabler]), and Kendrys Morales([@sec-morales]).

@@

Furthermore, we chose to examine $\pi_{nip}$ relative to centered age for all player. This is because centered age corresponds directly to the parameters $\beta, \eta,$ and $\xi$ in our model ([@eq-model]). It should be obvious why centered age corresponds to $\beta$ and $\eta$. However, the reason we know that centered age corresponds to $\xi$ directly is because players are only an age for one season. Thus, if we are given a year and player $n$'s corresponding age we can deduce the year for all ages of the player. This means that the year-over-year effect, which $\xi$ captures, is directly present in the figures. The parameters $\alpha$ and $\delta$ work more in the background of the predictions presented in the figures. We leave the discussion of each to when they appear in the figures of certain players.

## Data

Similar to Fellingham and Fisher (2017), we have used the Lahman data set for player statistics. While Lahman has data on a wide range of MLB realted topics, we decided to focus on a singular data sheet. We focused on the "Batting" data set in Lahman which describes player-year-team batting statistics. That is, each entry in Batting is for a player $n$ who played in year $i$ for team $t$. This allows multiple entries for the same year for the same player if they were traded, which is important for our analysis because different teams implies different home ballparks.

In order to be considered in our analysis a player had to be in Batting and have played for at least 6 seasons from 1973-2019. We chose these cut-offs because in 1973 the American League allowed the Designated Hitter, signaling that there would be an increased specialization in labor for hitting. We chose 2019 as the other cut-off because 2020 was the COVID season which was drastically shortened and very different compared to almost all other previous seasons. Furthermore, in order to be considered in our analysis players had to have had at least 50 AB's across those 6 seasons played. The effect of these cut-offs was that we were left with players who had longer careers and who hit HR's. There were many players dropped who never hit HR's because of their short stints which made prediction hard and prediction for these playes did not seem fruitful given their general inconsequential careers.

@@

Friendly, M., Dalzell, C., Monkman, M., & Murphy, D. (2022). Lahman: Sean 'lahman' 27 baseball database. <https://CRAN.R-project.org/package=Lahman>
